---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# EQvalue


## Overview

EQvalue is an R package to calculate Quality Adjusted Life Year's (QALY) from [EuroQol questionaire EQ-5D-5L](https://euroqol.org/eq-5d-instruments/eq-5d-5l-about/) 


## Installation
```{r, eval = FALSE}
# The easiest way to install:
devtools::install_github("HaemAalborg/EQvalue")
```


## Usage
EQ-5D-5L data looks something like this
```{r echo=FALSE}
NAME     <- c("Hansen","Jensen","Olesen")

MOBILITY <- c(1,2,2)
SELFCARE <- c(1,3,5)
ACTIVITY <- c(1,2,4)
PAIN     <- c(1,3,3)
ANXIETY  <- c(1,2,1)

df_0 <- data.frame(NAME, MOBILITY, SELFCARE, ACTIVITY, PAIN, ANXIETY)
df_0
```


The function `EQpaste` gathers the answers into one column if they corronspond to the naming scheeme proposed in the user guide, which is: MOBILITY, SELFCARE, ACTIVITY, PAIN, ANXIETY.
```{r}
library(EQvalue)

df_1 <- EQpaste(df_0)
df_1
```


The function is called `QALY` and takes as arguments a dataframe, a country and a name of the colum with the parsed scores eg. 11111.
```{r example}
df_2 <- QALY(df_1, country = "dk", name = "STATE")
df_2
```





